---
title: "Hotel Review's Analysis"
author: "Tommaso Comelli"
date: "06/07/2021"

output: 
 revealjs::revealjs_presentation:
    transition: zoom
    center: true
    overview: true
    navigationMode: 'default'
css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(png)
library(grid)
library(knitr)
library(readr)
library(plotly)
library(ggplot2)
library(tidyverse)
library(leaflet)
library(tidytext)
library(corrplot)
library(tm)
library(stopwords)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
```


<section>

## Introduzione

## Why this project

<div style="font-size: 30px; text-align:left; font-family: 'Times New Roman', Times, serif;">

The project I've decided to implent has the purpose to analyze some hotels client's reviews.All of us have at least once reviewed, positively or negatively, a hotel because we were struck by certain peculiarities of the structure.

Above all, however, before booking any hotel each of us read all the reviews in detail to understand whether or not to book. But have you ever wondered what all reviews have in common?

I have, and I would like to solve this doubt.

</div>


## The dataset

<p style="font-size: 30px; text-align:left; font-family: 'Times New Roman', Times, serif;">
I found the daset I used on kaggle.com and is named "hotel_reviews.csv". The daset contains 512k reviews of some clients reguarding about 1500 luxury hotels all over Europe. The dataset is composed by 17 fields which are shown below
</p>

```{r}
reviews<-read.csv("Hotel_Reviews.csv")
hreviews<-data.frame(reviews)

```
<div style="font-size: 30px; text-align:left; font-family: 'Times New Roman', Times, serif;">

  + _Hotel_Name_: name of the hotel
  + _Hotel_Address_: address of the hotel
  + _Reviewer_Nationality_: nationality of the client
  + _Negative_Review_: negative review
  + _Positive_Review_: negative review
  + _ReviewTotalNegativeWordCounts_: num. of words in PR
  + _ReviewTotalPositiveWordCounts_:   num. of words in PR
  + _Reviewer_Score_: score assigned from the client 
  + _TotalNumberof_Reviews_: Amount of the reviews per hotel
  + _lat_:latitude of the hotel
  + _long_: longitude of the hotel
  
</div>

## Question to answer

<div style="font-size: 30px; text-align:left; font-family: 'Times New Roman', Times, serif;">

With a dataset so rich in information, many questions have arisen to understand the different relationships between reviews, these are the most important that I will deepen in the course of my project.

+ Which is the best luxury hotel in Europe?
+ Which is the worst luxury hotel?
+ Is there any correlation between the client's nationality and the rating assigned to the hotel?
+ What are the words customers use most frequently for negative and positive reviews?
+ What is the average number of words of a review (positive and negative)?

</div>

</section>

## 

<section>

## An eye on the dataset 

```{r}
hreviews2<-hreviews %>%
          select(Hotel_Address, 
                 Additional_Number_of_Scoring, 
                 Average_Score, 
                 Hotel_Name,
                 Total_Number_of_Reviews,
                 lat,
                 lng)

values<- c(348,262,214,236,422)
region<-c("Spain","Italy","Netherlands","Austria","UK")
data<-data.frame(region, values)

mapdata<-map_data("world")
mapdata<-left_join(mapdata,data, by="region")
mapdata1<-mapdata %>% filter(region=="Austria" |
                               region=="Belgium" |
                               region=="Bulgaria" |
                               region=="Croatia" |
                               region=="Cyprus" |
                               region=="Czech Republic" |
                               region=="Denmark" |
                               region=="Finland" |
                               region=="Estonia" |
                               region=="France" |
                               region=="Germany" |
                               region=="Greece" |
                               region=="Hungary" |
                               region=="Ireland" |
                               region=="Italy" |
                               region=="Latvia" |
                               region=="Lithuania" |
                               region=="Luxembourg" |
                               region=="Malta" |
                               region=="UK" |
                               region=="Netherlands" |
                               region=="Poland" |
                               region=="Portugal" |
                               region=="Romania" |
                               region=="Slovakia" |
                               region=="Slovenia" |
                               region=="Spain" |
                               region=="Sweden")

ggplot(mapdata1, aes(x=long,y=lat, group=group))+
  geom_polygon(aes(fill=values))

```


## View

<div style="margin-left:100px;">

```{r}
values<- c(348,262,214,236,422)
region<-c("Spain","Italy","Netherlands","Austria","UK")
plot_ly(type='pie', labels=region, values=values, textinfo='percent', insidetextorientation='radial')

```

</div>


</section>
##
<section style="background:none; border:none; box-shadow:none; ">

## Distribution

<div style="margin-left:100px;">

```{r}
 latandlong<-hreviews%>%
                group_by(Hotel_Address,
                         Hotel_Name,Average_Score,
                         Total_Number_of_Reviews,
                         lat,
                         lng) %>%
                summarize(latitude=mean(lat), .groups = 'drop')



```

## Spain distribution

<div style="margin-left:100px;">


```{r}
hotelSpagna<-latandlong%>%
                filter((between(lat,41,41.5)))


leaflet(data = hotelSpagna) %>% addTiles() %>% addMarkers(~lng, ~lat, popup = ~as.character(Hotel_Name))

```
</div>

## Italy distribution
<div style="margin-left:100px;">

```{r}
hotelItalia<-latandlong%>%
                filter((between(lat,45,46)))


leaflet(data = hotelItalia) %>% addTiles() %>%
  addMarkers(~lng, ~lat, popup = ~as.character(Hotel_Name))
```




</div>

```{r}
hreviews3<- hreviews2 %>%
            group_by(Hotel_Address,
                         Hotel_Name,Average_Score,
                         Total_Number_of_Reviews,
                         lat,
                         lng)%>%
            summarize(mean_sc=mean(Average_Score), .groups='drop')
```
</section>

## 

<section>

## Global Rank

## Best
```{r}
 classifica1 <- arrange(hreviews3,-mean_sc)

  podio1<-classifica1%>%head(3)
  
  po1<-data.frame(podio1$Hotel_Name,podio1$mean_sc)

  ggplot(po1, aes(x=podio1$Hotel_Name, y=podio1$mean_sc)) + 
  geom_bar(stat = "identity", width=0.5, fill="light green") +
    xlab("Hotel Name")+
    ylab("Average Score")+
    coord_flip()+
    theme(legend.position="none")
```


## Worst 

```{r}
 classifica2<- arrange(hreviews3,desc(-mean_sc))
 podio2<- classifica2%>%head(3)
 
 po2<-data.frame(podio2$Hotel_Name,podio2$mean_sc)

  ggplot(po2, aes(x=podio2$Hotel_Name, y=podio2$mean_sc)) + 
  geom_bar(stat = "identity", width=0.5, fill="#f7595c") +
    xlab("Hotel Name")+
    ylab("Average Score")+
    coord_flip()+
    theme(legend.position="none")
   
```

## Weighted rank
```{r}
classpond<-
  mutate(hreviews3, meanpond=((mean_sc*Total_Number_of_Reviews)/516000))
```

## Best

```{r}

classifica3<- arrange(classpond,-meanpond)
 podio3<- classifica3%>%head(3)
 
 
 po3<-data.frame(podio3$Hotel_Name,podio3$meanpond)

  ggplot(po2, aes(x=podio3$Hotel_Name, y=podio3$meanpond)) + 
  geom_bar(stat = "identity", width=0.5, fill="light green") +
    xlab("Hotel Name")+
    ylab("Average Score")+
    coord_flip()+
    theme(legend.position="none")
 
```


## Worst

```{r}
 newclass2<- arrange(classpond,desc(-meanpond))
 podio4<- newclass2%>%head(3)
 
   
  po4<-data.frame(podio4$Hotel_Name,podio4$meanpond)

  ggplot(po4, aes(x=podio4$Hotel_Name, y=podio4$meanpond)) + 
  geom_bar(stat = "identity", width=0.5, fill="#f7595c") +
    xlab("Hotel Name")+
    ylab("Average Score")+
    coord_flip()+
    theme(legend.position="none")

```

## Rank by area 

## Spain podium

## Best
```{r}

classSp<-
  mutate(hotelSpagna, meanpond=((Average_Score*Total_Number_of_Reviews)/516000))

  newclasssp<- arrange(classSp,-meanpond)
  
  podio<-newclasssp%>%head(3)
  
  po<-data.frame(podio$Hotel_Name,podio$meanpond)
  col<-c("#ffc400","#c60b1e","#c60b1e")
  ggplot(po, aes(x=podio$Hotel_Name, y=podio$meanpond)) + 
  geom_bar(stat = "identity", width=0.5, fill=col) +
    xlab("Hotel Name")+
    ylab("Average Score")+
    coord_flip()+
    theme(legend.position="none")

```


## Italy Podium

## Best
```{r}

classIt<-
  mutate(hotelItalia, meanpond=((Average_Score*Total_Number_of_Reviews)/516000))

  newclassit<- arrange(classIt,-meanpond)

 podio5<-newclassit%>%head(3)
 col<-c("white","red","dark green")
 po5<-data.frame(podio5$Hotel_Name,podio5$meanpond)
  ggplot(po5, aes(x=podio5$Hotel_Name, y=podio5$meanpond)) + 
  geom_bar(stat = "identity", width=0.5, fill=col) +
    xlab("Hotel Name")+
    ylab("Average Score")+
    theme(legend.position="none")
```
</section>
## 

<section>

## An eye on the reviewer's

<div style="margin-left:100px;">

```{r}
prov<-hreviews%>%select(Reviewer_Nationality)
frequency_prov = prov %>% count(Reviewer_Nationality) %>% arrange(desc(n))

fig <- frequency_prov %>% plot_ly(labels = ~Reviewer_Nationality, values = ~n)
fig <- fig %>% add_pie(hole = 0.5)
fig <- fig %>% layout(showlegend = F,
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
```
</div>
</section>
## 

<section>

## Spain Correlation 
 
```{r}
hotelSpagna2<-hreviews%>%
  select(Hotel_Name,Reviewer_Nationality,Reviewer_Score,lat,lng
)
hotelSpagna3<-hotelSpagna2%>% 
  filter((between(lat,41,41.5)))


prova<- filter(hotelSpagna3,Hotel_Name=="Sansi Diputacio")
ggplot(prova, aes(Reviewer_Score , Reviewer_Nationality)) + geom_point()+ylab("Reviewer Nationality")+xlab("Reviewer Score")

# linear model 
mod1 = lm(Reviewer_Score~Reviewer_Nationality, data = prova)

```

## 

```{r}

ggplot(prova,aes(Reviewer_Score , Reviewer_Nationality)) + 
  geom_point() + 
  geom_abline(intercept = mod1$coefficients[1], 
              slope = mod1$coefficients[2], 
              color = "red")+ylab("Reviewer Nationality")+xlab("Reviewer Score")
```

## Italy Correlation

```{r}
hotelItalia2<-hreviews%>%
  select(Hotel_Name,Reviewer_Nationality,Reviewer_Score,lat,lng
)
hotelItalia3<-hotelItalia2%>% 
  filter((between(lat,45,46)))


prova<- filter(hotelItalia3,Hotel_Name=="Hotel VIU Milan")
ggplot(prova, aes(Reviewer_Score , Reviewer_Nationality)) + geom_point()+ylab("Reviewer Nationality")+xlab("Reviewer Score")
```

## 

```{r}
# linear model 
mod1 = lm(Reviewer_Score~Reviewer_Nationality, data = prova)

ggplot(prova,aes(Reviewer_Score , Reviewer_Nationality)) + 
  geom_point() + 
  geom_abline(intercept = mod1$coefficients[1], 
              slope = mod1$coefficients[2], 
              color = "red")+ylab("Reviewer Nationality")+xlab("Reviewer Score")
```



## Second Correlation

```{r}
hotelSpagna2<-hreviews%>%
  select(Hotel_Name,Review_Total_Positive_Word_Counts,Reviewer_Score,lat,lng)

hotelSpagna3<-hotelSpagna2%>% 
  filter((between(lat,41,41.5)))


prova<- filter(hotelSpagna3,Hotel_Name=="Sansi Diputacio")
ggplot(prova, aes( Review_Total_Positive_Word_Counts, Reviewer_Score)) + geom_point()+xlab("N.of words")+ylab("Reviewer Score")

# linear model 
mod1 = lm(Review_Total_Positive_Word_Counts ~ Reviewer_Score, data = prova)

```

## 

```{r}
ggplot(prova,aes(Review_Total_Positive_Word_Counts, Reviewer_Score)) + 
  geom_point() + 
  geom_abline(intercept = mod1$coefficients[1], 
              slope = mod1$coefficients[2], 
              color = "red")+xlab("N. Of words")+ylab("Reviewer Score")

```


## In general


```{r}

hreviewscorr<- hreviews%>% select(Reviewer_Score,Average_Score, Total_Number_of_Reviews, Review_Total_Positive_Word_Counts,Review_Total_Negative_Word_Counts)

colnames(hreviewscorr)<- c("Punteggio","Media","NTotRev", "NParoleRp", "NParoleRn")

corr <- round(cor(hreviewscorr), 1)

corrplot(corr, method="shade")

```
</section>
## 

<section>

## Text Analysis

```{r}
recensioni<- hreviews %>% select(Positive_Review, Review_Total_Positive_Word_Counts, Negative_Review, Review_Total_Negative_Word_Counts)
```

## First Text Analysis

```{r}
par(mfrow=c(1,2))
boxplot(recensioni$Review_Total_Negative_Word_Counts, varwidth=TRUE,outwex=TRUE, main="Negative Review", outline=FALSE)
boxplot(recensioni$Review_Total_Positive_Word_Counts, varwidth=TRUE, main="Positive Review", outline=FALSE)


```

## The numbers

```{r}
summary(recensioni$Review_Total_Positive_Word_Counts)
summary(recensioni$Review_Total_Negative_Word_Counts)
```
</section>
## 

<section>

## Detailed Analysis

## Positive Reviews


```{r}

text_df <- tibble(line = 1:515738, text = recensioni$Positive_Review)
rus_stopwords = data.frame(word = stopwords("ru"))


new_df <- text_df %>% unnest_tokens(word, text)

new_df1<-new_df %>%
  filter(!(word %in% stopwords("english")))

frequency_dataframe = new_df1 %>% count(word) %>% arrange(desc(n))

short_dataframe = head(frequency_dataframe, 25)
ggplot(short_dataframe, aes(x = word, y = n, fill = word),ylab="") +theme(axis.text.x = element_text(angle = 90))+ geom_col() +ylab("Freq")
```

## Graphic Rappresentation

```{r}
wordcloud(words = frequency_dataframe$word, freq = frequency_dataframe$n, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

## Negative Reviews
```{r}
text_df <- tibble(line = 1:515738, text = recensioni$Negative_Review)
rus_stopwords = data.frame(word = stopwords("ru"))

new_df <- text_df %>% unnest_tokens(word, text)

new_df1<-new_df %>%
  filter(!(word %in% stopwords("english")))

frequencyn_dataframe = new_df1 %>% count(word) %>% arrange(desc(n))

short_dataframe = head(frequencyn_dataframe, 25)
ggplot(short_dataframe, aes(x = word, y = n, fill = word),ylab="") +theme(axis.text.x = element_text(angle = 90))+ geom_col() +ylab("Freq")
```

## Graphic Rappresentation
```{r}
wordcloud(words = frequencyn_dataframe$word, freq = frequency_dataframe$n, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```
</section>

##

<section>
<h1> The end</h1>
<h2>Thanks for the attention</h2>
</section>

